---
title: "Project 2"
output: html_document
---

```{r}
library(ggplot2)
library(caret)
library(plyr)
library(dplyr)
file <- "~/University/Semester 10/Data Science/Final Project/train.csv"
train <- read.csv(file, encoding="UTF-8")

 file <- "~/University/Semester 10/Data Science/Final Project/test.csv"
test <- read.csv(file, encoding="UTF-8")

train$TARGET = as.factor(train$TARGET)

```

#1 First Prediction
```{r}
# Features: "sum_USAGE","avg_USAGE", "weighted_avg_USAGE"
# Weighted average usage is the weighted average for the 5 months usage with the higher weights given to the nearest months to the 6th month. The last month gets the highest weight: 5

train$sum_USAGE = train$X206_USAGE + train$X207_USAGE + train$X208_USAGE + train$X209_USAGE + train$X210_USAGE

train$avg_USAGE = rowMeans(subset(train, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE, X210_USAGE)), na.rm = TRUE)

train$weighted_avg_USAGE =  apply(subset(train, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE, X210_USAGE)), 1, function(d) weighted.mean(d, c(1,2,3,4,5), na.rm = TRUE))

 keep <- c("sum_USAGE", "TARGET")
train_sum <- train[keep]

keep <- c("avg_USAGE", "TARGET")
train_avg <- train[keep]

keep <- c("weighted_avg_USAGE", "TARGET")
train_w_avg <- train[keep]



test$sum_USAGE = test$X206_USAGE + test$X207_USAGE + test$X208_USAGE + test$X209_USAGE + test$X210_USAGE

test$weighted_avg_USAGE =  apply(subset(test, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE, X210_USAGE)), 1, function(d) weighted.mean(d, c(1,2,3,4,5), na.rm = TRUE))
 
keep <- c("sum_USAGE")
test_sum <- test[keep]
keep <- c("avg_USAGE")
test_avg <- test[keep]
keep <- c("weighted_avg_USAGE")
test_w_avg <- test[keep]

sumFit <- train(TARGET ~ .,method="J48",data=train_sum)
sumPrediction <- predict(sumFit,newdata=test_sum)

avgFit <- train(TARGET ~ .,method="J48",data=train_avg)
avgPrediction <- predict(avgFit,newdata=test_avg)

weightedAvgFit <- train(TARGET ~ .,method="J48",data=train_w_avg)
weightedAvgPrediction <- predict(weightedAvgFit, newdata=test_w_avg)


keep <- c("sum_USAGE","avg_USAGE", "weighted_avg_USAGE", "TARGET")
train_custom <- train[keep]
keep <- c("sum_USAGE","avg_USAGE", "weighted_avg_USAGE")
test_custom <- test[keep]
customFit <- train(TARGET ~ .,method="J48",data=train_custom)
customPrediction <- predict(customFit,newdata=test_custom)

customPredictionDF <- as.data.frame(test$CONTRACT_KEY , customPrediction)
customPredictionDF$prediction <- customPrediction
colnames(customPredictionDF) <- c("CONTRACT_KEY", "PREDICTED_TARGET")

setwd("~/Desktop/DataScience Project2/")
write.csv(customPredictionDF, file = "earlyPredictions.csv", row.names=FALSE)
```


# Data exploration of the effect of the number of cells used by an account on the TARGET, Partitioning Training Data and measuring the accuracy by constructing the prediction table 
```{r}
#Failed Trial because the number of used cells didn't show much correlation with the TARGET as seen in the plotted graph and the produced prediciton table 

file <- "~/University/Semester 10/Data Science/Final Project/daily_aggregate.csv"
daily_aggregate <- read.csv(file, encoding="UTF-8")
file <- "~/University/Semester 10/Data Science/Final Project/calendar_ref.csv"
calendar_ref <- read.csv(file, encoding="UTF-8")

cells_quantitiy <- with(daily_aggregate, tapply(CELL_KEY, CONTRACT_KEY, FUN = function(x) length(unique(x))))

cells_count<-adply(cells_quantitiy, c(1))
colnames(cells_count) <- c("CONTRACT_KEY", "CELL_COUNT")

cells_count_train <- merge(train, cells_count, by="CONTRACT_KEY")
 
keep <- c("CONTRACT_KEY", "CELL_COUNT", "TARGET")
cells_count_train <- cells_count_train[keep]
ggplot(cells_count_train, aes(x=CONTRACT_KEY, y=CELL_COUNT, color=TARGET)) + geom_point()

cells_count_train$TARGET = as.factor(cells_count_train$TARGET)

inTrain <- createDataPartition(y=cells_count_train$TARGET,p=0.7, list=FALSE)
cells_count_training_set <- cells_count_train[inTrain,]
cells_count_testing_set <- cells_count_train[-inTrain,]
cellsCountPrediction <- predict(cellsCountFit, cells_count_testing_set[,1:2])

 cells_count_prediction_table <- table(cellsCountPrediction, cells_count_testing_set$TARGET)
cells_count_prediction_table 

```

#2 Second Prediction
```{r}
# Features: "avg_USAGE", "fifthMonth_TARGET"
# fifthMonth_Target indicates whether a customer exceeds their average usage over the first 4 months by 500 Mega Bytes in the fifth month.

train$avg_USAGE = rowMeans(subset(train, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE, X210_USAGE)), na.rm = TRUE)

train$fourMonths_avg_USAGE = rowMeans(subset(train, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE)), na.rm = TRUE)

train$fifthMonth_TARGET <- ifelse(train$X210_USAGE > train$fourMonths_avg_USAGE + 500, 1, 0)

keep <- c("avg_USAGE", "fifthMonth_TARGET", "TARGET")
train_custom2 <- train[keep]
custom2FinalFit <- train(TARGET ~ .,method="J48",data=train_custom2)

test$avg_USAGE = rowMeans(subset(test, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE, X210_USAGE)), na.rm = TRUE)

test$fourMonths_avg_USAGE = rowMeans(subset(test, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE)), na.rm = TRUE)

test$fifthMonth_TARGET <- ifelse(test$X210_USAGE > test$fourMonths_avg_USAGE + 500, 1, 0)

keep <- c("avg_USAGE", "fifthMonth_TARGET")
test_custom2 <-test[keep]

custom2Prediction <- predict(custom2FinalFit,newdata=test_custom2)
custom2PredictionDF <- as.data.frame(test$CONTRACT_KEY)
custom2PredictionDF$prediction <- custom2Prediction

colnames(custom2PredictionDF) <- c("CONTRACT_KEY", "PREDICTED_TARGET")
setwd("~/Desktop/DataScience Project2/")

write.csv(custom2PredictionDF, file = "custom2Predictions.csv", row.names=FALSE)

```

#3 Third Prediction
```{r}

# Features: "avg_USAGE", "fifthMonth_TARGET", "VALUE_SEGMENT"

train$avg_USAGE = rowMeans(subset(train, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE, X210_USAGE)), na.rm = TRUE)

train$fourMonths_avg_USAGE = rowMeans(subset(train, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE)), na.rm = TRUE)

train$fifthMonth_TARGET <- ifelse(train$X210_USAGE > train$fourMonths_avg_USAGE + 500, 1, 0)

test$avg_USAGE = rowMeans(subset(test, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE, X210_USAGE)), na.rm = TRUE)

test$fourMonths_avg_USAGE = rowMeans(subset(test, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE)), na.rm = TRUE)

test$fifthMonth_TARGET <- ifelse(test$X210_USAGE > test$fourMonths_avg_USAGE + 500, 1, 0)

file <- "~/University/Semester 10/Data Science/Final Project/contract_ref.csv"
contact_ref <- read.csv(file, encoding="UTF-8")

train_custom3 <- merge(train, contact_ref, by="CONTRACT_KEY")
test_custom3 <- merge(test, contact_ref, by="CONTRACT_KEY")

keep <- c("avg_USAGE", "fifthMonth_TARGET", "VALUE_SEGMENT", "TARGET")
train_custom3 <- train_custom3[keep]
keep <- c("avg_USAGE", "fifthMonth_TARGET", "VALUE_SEGMENT")
test_custom3 <- test_custom3[keep]
train_custom3[is.na(train_custom3)] <- "N/A"
test_custom3[is.na(test_custom3)] <- "N/A"

custom3Fit <- train(TARGET ~ .,method="J48",data=train_custom3)

custom3Prediction <- predict(custom3Fit,newdata=test_custom3)
custom3PredictionDF <- as.data.frame(test$CONTRACT_KEY)
custom3PredictionDF$prediction <- custom3Prediction

colnames(custom3PredictionDF) <- c("CONTRACT_KEY", "PREDICTED_TARGET")
setwd("~/Desktop/DataScience Project2/")

write.csv(custom3PredictionDF, file = "custom3Predictions.csv", row.names=FALSE)

```

#4 Fourth Prediction:
```{r}
# Features: "avg_USAGE", "fifthMonth_TARGET", "VALUE_SEGMENT", "AGE"

train$avg_USAGE = rowMeans(subset(train, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE, X210_USAGE)), na.rm = TRUE)

train$fourMonths_avg_USAGE = rowMeans(subset(train, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE)), na.rm = TRUE)

train$fifthMonth_TARGET <- ifelse(train$X210_USAGE > train$fourMonths_avg_USAGE + 500, 1, 0)

test$avg_USAGE = rowMeans(subset(test, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE, X210_USAGE)), na.rm = TRUE)

test$fourMonths_avg_USAGE = rowMeans(subset(test, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE)), na.rm = TRUE)

test$fifthMonth_TARGET <- ifelse(test$X210_USAGE > test$fourMonths_avg_USAGE + 500, 1, 0)

file <- "~/University/Semester 10/Data Science/Final Project/contract_ref.csv"
contact_ref <- read.csv(file, encoding="UTF-8")

train_custom4 <- merge(train, contact_ref, by="CONTRACT_KEY")
test_custom4 <- merge(test, contact_ref, by="CONTRACT_KEY")

keep <- c("avg_USAGE", "fifthMonth_TARGET", "VALUE_SEGMENT", "AGE", "TARGET")
train_custom4 <- train_custom4[keep]
keep <- c("avg_USAGE", "fifthMonth_TARGET", "VALUE_SEGMENT", "AGE")
test_custom4 <- test_custom4[keep]
train_custom4[is.na(train_custom4)] <- "N/A"
test_custom4[is.na(test_custom4)] <- "N/A"

custom4Fit <- train(TARGET ~ .,method="lda",data=train_custom4)

custom4Prediction <- predict(custom4Fit,newdata=test_custom4)
custom4PredictionDF <- as.data.frame(test$CONTRACT_KEY)
custom4PredictionDF$prediction <- custom4Prediction

colnames(custom4PredictionDF) <- c("CONTRACT_KEY", "PREDICTED_TARGET")
setwd("~/Desktop/DataScience Project2/")

write.csv(custom4PredictionDF, file = "custom4Predictions.csv", row.names=FALSE)
 
```

# Data partioning, training and testing to measure accuracies of  different algorithms
```{r}

# Accuracy: lda= 0.8068, J48(C4.5 Trees)= 0.8099, C5.0TREE= 0.809599,  glm= 0.8
#C4.5 Trees scored the highest accuracy.Thus, it is used in the fifth prediction

train$avg_USAGE = rowMeans(subset(train, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE, X210_USAGE)), na.rm = TRUE)

train$fourMonths_avg_USAGE = rowMeans(subset(train, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE)), na.rm = TRUE)

train$fifthMonth_TARGET <- ifelse(train$X210_USAGE > train$fourMonths_avg_USAGE + 500, 1, 0)

test$avg_USAGE = rowMeans(subset(test, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE, X210_USAGE)), na.rm = TRUE)

test$fourMonths_avg_USAGE = rowMeans(subset(test, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE)), na.rm = TRUE)

test$fifthMonth_TARGET <- ifelse(test$X210_USAGE > test$fourMonths_avg_USAGE + 500, 1, 0)

file <- "~/University/Semester 10/Data Science/Final Project/contract_ref.csv"
contact_ref <- read.csv(file, encoding="UTF-8")


inTrain <- createDataPartition(y=train$TARGET,p=0.7, list=FALSE)
train_4 <- train[inTrain,]
test_4 <- train[-inTrain,]

train_custom4 <- merge(train_4, contact_ref, by="CONTRACT_KEY")
test_custom4 <- merge(test_4, contact_ref, by="CONTRACT_KEY")

keep <- c("avg_USAGE", "fifthMonth_TARGET", "VALUE_SEGMENT", "AGE", "TARGET")
train_custom4 <- train_custom4[keep]
test_custom4 <- test_custom4[keep]
train_custom4[is.na(train_custom4)] <- "N/A"
test_custom4[is.na(test_custom4)] <- "N/A"

custom4Fit <- train(TARGET ~ .,method="J48",data=train_custom4)

custom4Prediction <- predict(custom4Fit,newdata=test_custom4[,1:4])

prediction_table4 <- table(custom4Prediction, test_custom4$TARGET)
accuracy <- (prediction_table4[1]+prediction_table4[4])/(prediction_table4[1]+prediction_table4[2] + prediction_table4[3]+prediction_table4[4])

```

#5 Fifth Prediction:
```{r}
# Features: "avg_USAGE", "fifthMonth_TARGET", "VALUE_SEGMENT", "AGE"

train$avg_USAGE = rowMeans(subset(train, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE, X210_USAGE)), na.rm = TRUE)

train$fourMonths_avg_USAGE = rowMeans(subset(train, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE)), na.rm = TRUE)

train$fifthMonth_TARGET <- ifelse(train$X210_USAGE > train$fourMonths_avg_USAGE + 500, 1, 0)

test$avg_USAGE = rowMeans(subset(test, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE, X210_USAGE)), na.rm = TRUE)

test$fourMonths_avg_USAGE = rowMeans(subset(test, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE)), na.rm = TRUE)

test$fifthMonth_TARGET <- ifelse(test$X210_USAGE > test$fourMonths_avg_USAGE + 500, 1, 0)

file <- "~/University/Semester 10/Data Science/Final Project/contract_ref.csv"
contact_ref <- read.csv(file, encoding="UTF-8")

train_custom5 <- merge(train, contact_ref, by="CONTRACT_KEY")
test_custom5 <- merge(test, contact_ref, by="CONTRACT_KEY")

keep <- c("avg_USAGE", "fifthMonth_TARGET", "VALUE_SEGMENT", "AGE", "TARGET")
train_custom5 <- train_custom5[keep]
keep <- c("avg_USAGE", "fifthMonth_TARGET", "VALUE_SEGMENT", "AGE")
test_custom5 <- test_custom5[keep]
train_custom5[is.na(train_custom5)] <- "N/A"
test_custom5[is.na(test_custom5)] <- "N/A"

custom5Fit <- train(TARGET ~ .,method="J48",data=train_custom5)

custom5Prediction <- predict(custom5Fit,newdata=test_custom5)
custom5PredictionDF <- as.data.frame(test$CONTRACT_KEY)
custom5PredictionDF$prediction <- custom5Prediction

colnames(custom5PredictionDF) <- c("CONTRACT_KEY", "PREDICTED_TARGET")
setwd("~/Desktop/DataScience Project2/")

write.csv(custom5PredictionDF, file = "custom5Predictions.csv", row.names=FALSE)

```

# Data partioning, training and testing to measure accuracies of  different algorithms with different set of features 
```{r}

# With features: "avg_USAGE", "weighted_avg_USAGE", "standard_diviation"
# Accuracies are : J48=.80274, lda=.8015, C5.0TREE=0.8015

# With features: "avg_USAGE", "weighted_avg_USAGE", "standard_diviation", "VALUE_SEGMENT", "AGE" 
# Accuracies are: C5.0TREE=0.800495, lda =.80182, J48=0.799611

# With features: "avg_USAGE", "weighted_avg_USAGE", "standard_diviation", "VALUE_SEGMENT"
# Accuracies are: J48 =0.803279, lda=.8035

# Accuracies didn't show much improvement to previous predictions so none of the above set of featueres was adopted

train$avg_USAGE = rowMeans(subset(train, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE, X210_USAGE)), na.rm = TRUE)

train$fourMonths_avg_USAGE = rowMeans(subset(train, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE)), na.rm = TRUE)

train$fifthMonth_TARGET <- ifelse(train$X210_USAGE > train$fourMonths_avg_USAGE + 500, 1, 0)

test$avg_USAGE = rowMeans(subset(test, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE, X210_USAGE)), na.rm = TRUE)

test$fourMonths_avg_USAGE = rowMeans(subset(test, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE)), na.rm = TRUE)

test$fifthMonth_TARGET <- ifelse(test$X210_USAGE > test$fourMonths_avg_USAGE + 500, 1, 0)

file <- "~/University/Semester 10/Data Science/Final Project/contract_ref.csv"
contact_ref <- read.csv(file, encoding="UTF-8")

train$weighted_avg_USAGE =  apply(subset(train, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE, X210_USAGE)), 1, function(d) weighted.mean(d, c(1,2,3,4,5), na.rm = TRUE))

train$standard_diviation = sqrt(((train$X206_USAGE-train$avg_USAGE)^2 + (train$X207_USAGE-train$avg_USAGE)^2 + (train$X208_USAGE-train$avg_USAGE)^2 + (train$X209_USAGE-train$avg_USAGE)^2 + (train$X210_USAGE-train$avg_USAGE)^2)/5)

inTrain <- createDataPartition(y=train$TARGET,p=0.7, list=FALSE)
train_6 <- train[inTrain,]
test_6 <- train[-inTrain,]

train_custom6 <- merge(train_6, contact_ref, by="CONTRACT_KEY")
test_custom6 <- merge(test_6, contact_ref, by="CONTRACT_KEY")

keep <- c("avg_USAGE", "weighted_avg_USAGE", "standard_diviation", "VALUE_SEGMENT", "TARGET")
train_custom6 <- train_custom6[keep]
test_custom6 <- test_custom6[keep]
train_custom6[is.na(train_custom6)] <- "N/A"
test_custom6[is.na(test_custom6)] <- "N/A"

custom6Fit <- train(TARGET ~ .,method="C5.0TREE",data=train_custom6)

custom6Prediction <- predict(custom6Fit,newdata=test_custom6[,1:4])

prediction_table6 <- table(custom6Prediction, test_custom6$TARGET)
accuracy <- (prediction_table6[1]+prediction_table6[4])/(prediction_table6[1]+prediction_table6[2] + prediction_table6[3]+prediction_table6[4])

```

#6 Sixth Prediction:
```{r}

# Features: "avg_USAGE", "weighted_avg_USAGE", "standard_deviation", "VALUE_SEGMENT", "fifthMonth_TARGET"
# Standard Deviation is the standard deviation of the usage across all months

train$avg_USAGE = rowMeans(subset(train, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE, X210_USAGE)), na.rm = TRUE)

train$fourMonths_avg_USAGE = rowMeans(subset(train, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE)), na.rm = TRUE)

train$fifthMonth_TARGET <- ifelse(train$X210_USAGE > train$fourMonths_avg_USAGE + 500, 1, 0)

test$avg_USAGE = rowMeans(subset(test, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE, X210_USAGE)), na.rm = TRUE)

test$fourMonths_avg_USAGE = rowMeans(subset(test, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE)), na.rm = TRUE)

test$fifthMonth_TARGET <- ifelse(test$X210_USAGE > test$fourMonths_avg_USAGE + 500, 1, 0)

file <- "~/University/Semester 10/Data Science/Final Project/contract_ref.csv"
contact_ref <- read.csv(file, encoding="UTF-8")

train$weighted_avg_USAGE =  apply(subset(train, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE, X210_USAGE)), 1, function(d) weighted.mean(d, c(1,2,3,4,5), na.rm = TRUE))

train$standard_diviation = sqrt(((train$X206_USAGE-train$avg_USAGE)^2 + (train$X207_USAGE-train$avg_USAGE)^2 + (train$X208_USAGE-train$avg_USAGE)^2 + (train$X209_USAGE-train$avg_USAGE)^2 + (train$X210_USAGE-train$avg_USAGE)^2)/5)

test$weighted_avg_USAGE =  apply(subset(test, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE, X210_USAGE)), 1, function(d) weighted.mean(d, c(1,2,3,4,5), na.rm = TRUE))

test$standard_diviation = sqrt(((test$X206_USAGE-test$avg_USAGE)^2 + (test$X207_USAGE-test$avg_USAGE)^2 + (test$X208_USAGE-test$avg_USAGE)^2 + (test$X209_USAGE-test$avg_USAGE)^2 + (test$X210_USAGE-test$avg_USAGE)^2)/5)

train_custom6 <- merge(train, contact_ref, by="CONTRACT_KEY")
test_custom6 <- merge(test, contact_ref, by="CONTRACT_KEY")

keep <- c("avg_USAGE", "weighted_avg_USAGE", "standard_diviation", "VALUE_SEGMENT", "fifthMonth_TARGET", "TARGET")
train_custom6 <- train_custom6[keep]
keep <- c("avg_USAGE", "weighted_avg_USAGE", "standard_diviation", "VALUE_SEGMENT", "fifthMonth_TARGET")
test_custom6 <- test_custom6[keep]
train_custom6[is.na(train_custom6)] <- "N/A"
test_custom6[is.na(test_custom6)] <- "N/A"

custom6Fit <- train(TARGET ~ .,method="lda",data=train_custom6)

custom6Prediction <- predict(custom6Fit,newdata=test_custom6)
custom6PredictionDF <- as.data.frame(test$CONTRACT_KEY)
custom6PredictionDF$prediction <- custom6Prediction

colnames(custom6PredictionDF) <- c("CONTRACT_KEY", "PREDICTED_TARGET")
setwd("~/Desktop/DataScience Project2/")

write.csv(custom6PredictionDF, file = "secondcustom6Predictions.csv", row.names=FALSE)

```

#7 Seventh Prediction:
```{r}

#Features: "avg_USAGE", "fifthMonth_TARGET", "VALUE_SEGMENT"

train$avg_USAGE = rowMeans(subset(train, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE, X210_USAGE)), na.rm = TRUE)

train$fourMonths_avg_USAGE = rowMeans(subset(train, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE)), na.rm = TRUE)

train$fifthMonth_TARGET <- ifelse(train$X210_USAGE > train$fourMonths_avg_USAGE + 500, 1, 0)

test$avg_USAGE = rowMeans(subset(test, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE, X210_USAGE)), na.rm = TRUE)

test$fourMonths_avg_USAGE = rowMeans(subset(test, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE)), na.rm = TRUE)

test$fifthMonth_TARGET <- ifelse(test$X210_USAGE > test$fourMonths_avg_USAGE + 500, 1, 0)

file <- "~/University/Semester 10/Data Science/Final Project/contract_ref.csv"
contact_ref <- read.csv(file, encoding="UTF-8")

train_custom7 <- merge(train, contact_ref, by="CONTRACT_KEY")
test_custom7 <- merge(test, contact_ref, by="CONTRACT_KEY")

keep <- c("avg_USAGE", "fifthMonth_TARGET", "VALUE_SEGMENT", "TARGET")
train_custom7 <- train_custom7[keep]
keep <- c("avg_USAGE", "fifthMonth_TARGET", "VALUE_SEGMENT")
test_custom7 <- test_custom7[keep]
train_custom7[is.na(train_custom7)] <- "N/A"
test_custom7[is.na(test_custom7)] <- "N/A"

custom7Fit <- train(TARGET ~ .,method="lda",data=train_custom7)

custom7Prediction <- predict(custom7Fit,newdata=test_custom7)
custom7PredictionDF <- as.data.frame(test$CONTRACT_KEY)
custom7PredictionDF$prediction <- custom7Prediction

colnames(custom7PredictionDF) <- c("CONTRACT_KEY", "PREDICTED_TARGET")
setwd("~/Desktop/DataScience Project2/")

write.csv(custom7PredictionDF, file = "custom7Predictions.csv", row.names=FALSE)

```

# Data partioning, training and testing to measure accuracies of  different algorithms
```{r}

#Accuracy J48= 0.611, which is very low compared to the previous measured accuracies

train$avg_USAGE = rowMeans(subset(train, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE, X210_USAGE)), na.rm = TRUE)

test$avg_USAGE = rowMeans(subset(test, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE, X210_USAGE)), na.rm = TRUE)

file <- "~/University/Semester 10/Data Science/Final Project/roaming_monthly.csv"
roaming_monthly <- read.csv(file, encoding="UTF-8")
 keep <- c("CONTRACT_KEY", "USAGE")
roaming_monthly_usage <- roaming_monthly[keep]
roaming_monthly_usage <- ddply(roaming_monthly_usage, "CONTRACT_KEY", numcolwise(sum))

train_roaming <- merge(train, roaming_monthly_usage, by="CONTRACT_KEY")
ggplot(train_roaming, aes(x=CONTRACT_KEY, y=USAGE, color=TARGET)) + geom_point()

inTrain <- createDataPartition(y=train_roaming$TARGET,p=0.7, list=FALSE)
train_8 <- train_roaming[inTrain,]
test_8 <- train_roaming[-inTrain,]

keep <- c("avg_USAGE", "USAGE", "TARGET")
train_custom8 <- train_8[keep]
test_custom8 <- test_8[keep]

custom8Fit <- train(TARGET ~ .,method="J48",data=train_custom8)

custom8Prediction <- predict(custom8Fit,newdata=test_custom8[,1:2])

prediction_table8 <- table(custom8Prediction, test_custom8$TARGET)
accuracy <- (prediction_table8[1]+prediction_table8[4])/(prediction_table8[1]+prediction_table8[2] + prediction_table8[3]+prediction_table8[4])

```

#9 Ninth Prediction:
```{r}

# Features: "avg_USAGE", "fifthMonth_TARGET", "VALUE_SEGMENT", "AGE", "NO_OF_SESSIONS"

file <- "~/University/Semester 10/Data Science/Final Project/daily_aggregate.csv"
daily_aggregate <- read.csv(file, encoding="UTF-8")

keep <- c("CONTRACT_KEY", "NO_OF_SESSIONS")
sessions_count <- daily_aggregate[keep]
sessions_count <- ddply(sessions_count, "CONTRACT_KEY", numcolwise(sum))

average_sessions_count <- mean(sessions_count$NO_OF_SESSIONS)

train_custom9 <- left_join(train, sessions_count, by="CONTRACT_KEY")
test_custom9 <- left_join(test, sessions_count, by="CONTRACT_KEY")
train_custom9[is.na(train_custom9)] <- average_sessions_count
test_custom9[is.na(test_custom9)] <- average_sessions_count

ggplot(train_custom9, aes(x=CONTRACT_KEY, y=NO_OF_SESSIONS, color=TARGET)) + geom_point()

train_custom9 <- merge(train_custom9, contact_ref, by="CONTRACT_KEY")
test_custom9 <- merge(test_custom9, contact_ref, by="CONTRACT_KEY")


keep <- c("avg_USAGE", "fifthMonth_TARGET", "VALUE_SEGMENT", "AGE", "NO_OF_SESSIONS", "TARGET")
train_custom9 <- train_custom9[keep]
keep <- c("avg_USAGE", "fifthMonth_TARGET", "VALUE_SEGMENT", "AGE", "NO_OF_SESSIONS")
test_custom9 <- test_custom9[keep]
train_custom9[is.na(train_custom9)] <- "N/A"
test_custom9[is.na(test_custom9)] <- "N/A"

custom9Fit <- train(TARGET ~ .,method="lda",data=train_custom9)

custom9Prediction <- predict(custom9Fit,newdata=test_custom9)
custom9PredictionDF <- as.data.frame(test$CONTRACT_KEY)
custom9PredictionDF$prediction <- custom9Prediction

colnames(custom9PredictionDF) <- c("CONTRACT_KEY", "PREDICTED_TARGET")
setwd("~/Desktop/DataScience Project2/")

write.csv(custom9PredictionDF, file = "custom9Predictions.csv", row.names=FALSE)


```

#10 Tenth Prediction:
```{r}

#10's features are the same as 9 Using the sessions count in the monthly aggregate adding the average number of sessions per account and the total usage over the 5 months

train$avg_SESSIONS <- rowMeans(subset(train, select = c(X206_SESSION_COUNT, X207_SESSION_COUNT, X208_SESSION_COUNT, X209_SESSION_COUNT, X210_SESSION_COUNT)), na.rm = TRUE)

test$avg_SESSIONS <- rowMeans(subset(test, select = c(X206_SESSION_COUNT, X207_SESSION_COUNT, X208_SESSION_COUNT, X209_SESSION_COUNT, X210_SESSION_COUNT)), na.rm = TRUE)

train$NO_OF_SESSIONS <- train$X206_SESSION_COUNT + train$X207_SESSION_COUNT + train$X208_SESSION_COUNT + train$X209_SESSION_COUNT + train$X210_SESSION_COUNT

train$TOTAL_USAGE <- train$X206_USAGE + train$X207_USAGE + train$X208_USAGE + train$X209_USAGE + train$X210_USAGE

test$NO_OF_SESSIONS <- test$X206_SESSION_COUNT + test$X207_SESSION_COUNT + test$X208_SESSION_COUNT + test$X209_SESSION_COUNT + test$X210_SESSION_COUNT

test$TOTAL_USAGE <- test$X206_USAGE + test$X207_USAGE + test$X208_USAGE + test$X209_USAGE + test$X210_USAGE


ggplot(train, aes(x=CONTRACT_KEY, y=NO_OF_SESSIONS, color=TARGET)) + geom_point()

train_custom10 <- merge(train, contact_ref, by="CONTRACT_KEY")
test_custom10 <- merge(test, contact_ref, by="CONTRACT_KEY")


keep <- c("avg_USAGE", "TOTAL_USAGE", "fifthMonth_TARGET", "VALUE_SEGMENT", "AGE", "NO_OF_SESSIONS", "avg_SESSIONS", "TARGET")
train_custom10 <- train_custom10[keep]
keep <- c("avg_USAGE", "TOTAL_USAGE", "fifthMonth_TARGET", "VALUE_SEGMENT", "AGE", "NO_OF_SESSIONS", "avg_SESSIONS")
test_custom10 <- test_custom10[keep]
train_custom10[is.na(train_custom10)] <- "N/A"
test_custom10[is.na(test_custom10)] <- "N/A"

custom10Fit <- train(TARGET ~ .,method="lda",data=train_custom10)

custom10Prediction <- predict(custom10Fit,newdata=test_custom10)
custom10PredictionDF <- as.data.frame(test$CONTRACT_KEY)
custom10PredictionDF$prediction <- custom10Prediction

colnames(custom10PredictionDF) <- c("CONTRACT_KEY", "PREDICTED_TARGET")
setwd("~/Desktop/DataScience Project2/")

write.csv(custom10PredictionDF, file = "custom10Predictions.csv", row.names=FALSE)

```

#11 Eleventh Prediction:
```{r}
# Features: "TOTAL_USAGE", "fifthMonth_TARGET", "VALUE_SEGMENT", "AGE", "NO_OF_SESSIONS"

train$NO_OF_SESSIONS <- train$X206_SESSION_COUNT + train$X207_SESSION_COUNT + train$X208_SESSION_COUNT + train$X209_SESSION_COUNT + train$X210_SESSION_COUNT

train$TOTAL_USAGE <- train$X206_USAGE + train$X207_USAGE + train$X208_USAGE + train$X209_USAGE + train$X210_USAGE

test$NO_OF_SESSIONS <- test$X206_SESSION_COUNT + test$X207_SESSION_COUNT + test$X208_SESSION_COUNT + test$X209_SESSION_COUNT + test$X210_SESSION_COUNT

test$TOTAL_USAGE <- test$X206_USAGE + test$X207_USAGE + test$X208_USAGE + test$X209_USAGE + test$X210_USAGE


train_custom11 <- merge(train, contact_ref, by="CONTRACT_KEY")
test_custom11 <- merge(test, contact_ref, by="CONTRACT_KEY")


keep <- c("TOTAL_USAGE", "fifthMonth_TARGET", "VALUE_SEGMENT", "AGE", "NO_OF_SESSIONS", "TARGET")
train_custom11 <- train_custom11[keep]
keep <- c("TOTAL_USAGE", "fifthMonth_TARGET", "VALUE_SEGMENT", "AGE", "NO_OF_SESSIONS")
test_custom11 <- test_custom11[keep]
train_custom11[is.na(train_custom11)] <- "N/A"
test_custom11[is.na(test_custom11)] <- "N/A"

custom11Fit <- train(TARGET ~ .,method="lda",data=train_custom11)

custom11Prediction <- predict(custom11Fit,newdata=test_custom11)
custom11PredictionDF <- as.data.frame(test$CONTRACT_KEY)
custom11PredictionDF$prediction <- custom11Prediction

colnames(custom11PredictionDF) <- c("CONTRACT_KEY", "PREDICTED_TARGET")
setwd("~/Desktop/DataScience Project2/")

write.csv(custom11PredictionDF, file = "custom11Predictions.csv", row.names=FALSE)

```

#12 Twelfth Prediction
```{r}
# Features: "TOTAL_USAGE", "fifthMonth_TARGET", "VALUE_SEGMENT", "AGE", "NO_OF_SESSIONS", "GENDER"

train$NO_OF_SESSIONS <- train$X206_SESSION_COUNT + train$X207_SESSION_COUNT + train$X208_SESSION_COUNT + train$X209_SESSION_COUNT + train$X210_SESSION_COUNT

train$TOTAL_USAGE <- train$X206_USAGE + train$X207_USAGE + train$X208_USAGE + train$X209_USAGE + train$X210_USAGE

test$NO_OF_SESSIONS <- test$X206_SESSION_COUNT + test$X207_SESSION_COUNT + test$X208_SESSION_COUNT + test$X209_SESSION_COUNT + test$X210_SESSION_COUNT

test$TOTAL_USAGE <- test$X206_USAGE + test$X207_USAGE + test$X208_USAGE + test$X209_USAGE + test$X210_USAGE

train$avg_USAGE = rowMeans(subset(train, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE, X210_USAGE)), na.rm = TRUE)

train$fourMonths_avg_USAGE = rowMeans(subset(train, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE)), na.rm = TRUE)

train$fifthMonth_TARGET <- ifelse(train$X210_USAGE > train$fourMonths_avg_USAGE + 500, 1, 0)

test$avg_USAGE = rowMeans(subset(test, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE, X210_USAGE)), na.rm = TRUE)

test$fourMonths_avg_USAGE = rowMeans(subset(test, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE)), na.rm = TRUE)

test$fifthMonth_TARGET <- ifelse(test$X210_USAGE > test$fourMonths_avg_USAGE + 500, 1, 0)

file <- "~/University/Semester 10/Data Science/Final Project/contract_ref.csv"
contact_ref <- read.csv(file, encoding="UTF-8")

train_custom12 <- merge(train, contact_ref, by="CONTRACT_KEY")
test_custom12 <- merge(test, contact_ref, by="CONTRACT_KEY")


keep <- c("TOTAL_USAGE", "fifthMonth_TARGET", "VALUE_SEGMENT", "AGE", "NO_OF_SESSIONS", "GENDER", "TARGET")
train_custom12 <- train_custom12[keep]
keep <- c("TOTAL_USAGE", "fifthMonth_TARGET", "VALUE_SEGMENT", "AGE", "NO_OF_SESSIONS", "GENDER")
test_custom12 <- test_custom12[keep]
train_custom12[is.na(train_custom12)] <- "N/A"
test_custom12[is.na(test_custom12)] <- "N/A"

custom12Fit <- train(TARGET ~ .,method="rf",data=train_custom12, tuneLength = 5,trControl = trainControl(method = "cv", indexOut = train))

custom12Prediction <- predict(custom12Fit,newdata=test_custom12)
custom12PredictionDF <- as.data.frame(test$CONTRACT_KEY)
custom12PredictionDF$prediction <- custom12Prediction

colnames(custom12PredictionDF) <- c("CONTRACT_KEY", "PREDICTED_TARGET")
setwd("~/Desktop/DataScience Project2/")

write.csv(custom12PredictionDF, file = "custom12Predictions.csv", row.names=FALSE)

```

#13 Thirteenth Prediction
```{r}

# Features: "X206_USAGE", "X207_USAGE", "X208_USAGE", "X209_USAGE", "X210_USAGE", "X206_SESSION_COUNT", "X207_SESSION_COUNT", "X208_SESSION_COUNT", "X209_SESSION_COUNT", "X210_SESSION_COUNT", "TOTAL_USAGE", "fifthMonth_TARGET", "VALUE_SEGMENT", "AGE", "NO_OF_SESSIONS", "GENDER"

# Not submitted due to shortage in computing power

train$NO_OF_SESSIONS <- train$X206_SESSION_COUNT + train$X207_SESSION_COUNT + train$X208_SESSION_COUNT + train$X209_SESSION_COUNT + train$X210_SESSION_COUNT

train$TOTAL_USAGE <- train$X206_USAGE + train$X207_USAGE + train$X208_USAGE + train$X209_USAGE + train$X210_USAGE

test$NO_OF_SESSIONS <- test$X206_SESSION_COUNT + test$X207_SESSION_COUNT + test$X208_SESSION_COUNT + test$X209_SESSION_COUNT + test$X210_SESSION_COUNT

test$TOTAL_USAGE <- test$X206_USAGE + test$X207_USAGE + test$X208_USAGE + test$X209_USAGE + test$X210_USAGE

train$avg_USAGE = rowMeans(subset(train, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE, X210_USAGE)), na.rm = TRUE)

train$fourMonths_avg_USAGE = rowMeans(subset(train, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE)), na.rm = TRUE)

train$fifthMonth_TARGET <- ifelse(train$X210_USAGE > train$fourMonths_avg_USAGE + 500, 1, 0)

test$avg_USAGE = rowMeans(subset(test, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE, X210_USAGE)), na.rm = TRUE)

test$fourMonths_avg_USAGE = rowMeans(subset(test, select = c(X206_USAGE, X207_USAGE, X208_USAGE, X209_USAGE)), na.rm = TRUE)

test$fifthMonth_TARGET <- ifelse(test$X210_USAGE > test$fourMonths_avg_USAGE + 500, 1, 0)

file <- "~/University/Semester 10/Data Science/Final Project/contract_ref.csv"
contact_ref <- read.csv(file, encoding="UTF-8")

train_custom13 <- merge(train, contact_ref, by="CONTRACT_KEY")
test_custom13 <- merge(test, contact_ref, by="CONTRACT_KEY")


keep <- c("X206_USAGE", "X207_USAGE", "X208_USAGE", "X209_USAGE", "X210_USAGE", "X206_SESSION_COUNT", "X207_SESSION_COUNT", "X208_SESSION_COUNT", "X209_SESSION_COUNT", "X210_SESSION_COUNT", "TOTAL_USAGE", "fifthMonth_TARGET", "VALUE_SEGMENT", "AGE", "NO_OF_SESSIONS", "GENDER", "TARGET")
train_custom13 <- train_custom13[keep]

keep <- c("X206_USAGE", "X207_USAGE", "X208_USAGE", "X209_USAGE", "X210_USAGE", "X206_SESSION_COUNT", "X207_SESSION_COUNT", "X208_SESSION_COUNT", "X209_SESSION_COUNT", "X210_SESSION_COUNT", "TOTAL_USAGE", "fifthMonth_TARGET", "VALUE_SEGMENT", "AGE", "NO_OF_SESSIONS", "GENDER")
test_custom13 <- test_custom13[keep]

train_custom13[is.na(train_custom13)] <- "N/A"
test_custom13[is.na(test_custom13)] <- "N/A"

custom13Fit <- train(TARGET ~ .,method="rf",data=train_custom13, tuneLength = 5,trControl = trainControl(method = "cv", indexOut = train))

custom13Prediction <- predict(custom13Fit,newdata=test_custom13)
custom13PredictionDF <- as.data.frame(test$CONTRACT_KEY)
custom13PredictionDF$prediction <- custom13Prediction

colnames(custom13PredictionDF) <- c("CONTRACT_KEY", "PREDICTED_TARGET")
setwd("~/Desktop/DataScience Project2/")

write.csv(custom13PredictionDF, file = "custom13Predictions.csv", row.names=FALSE)

```


